Sistema Online de Filtragem em um Ambiente com Alta Taxa de Eventos

### 2006-11-05 published.tex
Fix references and citations
git-svn-id: file:///Users/andre/svn/andre_phd/thesis/trunk@396 b2e9302d-b4d2-0310-80c4-8586bce995ec

\paragraph{Agosto de 2006: \sectioneng{Deployment of the ATLAS High-Level
Trigger}}, IEEE Transactions on Nuclear Science. Referência~\ref{aa:tns-06}

@@

\paragraph{Maio de 2006: \sectioneng{A configuration system for the ATLAS
trigger}}, Journal of Instrumentation, Maio de
2006. Referência~\ref{aa:jinst-06}

@@

\paragraph{Fevereiro de 2006: \setioneng{Testing on a Large Scale : running
the ATLAS Data Acquisition and High Level Trigger Software on 700 PC Nodes}}
Computing In High Energy and Nuclear Physics  CHEP 2006 , Mumbai, India , 13 -
17 Feb 2006. Referência~\cite{aa:chep-06-01}

@@

\begin{quotation}
The ATLAS experiment at the Large Hadron Collider (LHC) will face the
challenge of efficiently selecting interesting candidate events in pp
collisions at 14 TeV center of mass energy, while rejecting the enormous
number of background events, stemming from an interaction rate of up to 10^9
Hz. The First Level trigger will reduce this rate to around O(100
kHz). Subsequently, the High Level Trigger (HLT), which is comprised of the
Second Level trigger and the Event Filter, will need to further reduce this
rate by a factor of O(10^3). The HLT selection is software based and will be
implemented on commercial CPUs, using a common framework built on the standard
ATLAS object oriented software architecture. In this paper an overview of the
current implementation of the selection for electrons and photons in the HLT
is given. The performance of this implementation has been evaluated using
Monte Carlo simulations in terms of the efficiency for the signal channels,
rate expected for the selection, data preparation times, and algorithm
execution times. Besides the efficiency and rate estimates, some physics
examples will be discussed, showing that the triggers are well adapted for the
physics programme envisaged at LHC. The electron and photon trigger software
is also being exercised at the ATLAS 2004 Combined Test Beam, where components
from all ATLAS subdetectors are taking data together along the H8 SPS
extraction line; from these tests a validation of the selection architecture
chosen in a real on-line environment is expected.
\end{quotation}

\paragraph{Junho de 2004: \sectioneng{Algorithms for the ATLAS high-level
trigger}}. Referência~\cite{aa:tns-04-05}.

@@

\paragraph{Junho de 2004: \sectioneng{The base-line DataFlow system of the ATLAS
Trigger and DAQ}} Na revista \sectioneng{IEEE Transactions on Nuclear
Science}, volume 51, número 3. Referência \cite{aa:tns-2004-3}.

\begin{quotation}
\sectioneng{The base-line design and implementation of the ATLAS DAQ DataFlow
system is described. The main components realizing the DataFlow system, their
interactions, bandwidths and rates are being discussed and performance
measurements on a 10\% scale prototype for the final Atlas TDAQ DataFlow system
are presented. \\
This prototype is a combination of custom design components and of
multi-threaded software applications implemented in C++ and running in a Linux
environment on commercially available PCs interconnected by a fully switched
gigabit Ethernet network.}
\end{quotation}

\paragraph{Junho de 2004: \sectioneng{ATLAS TDAQ data collection software} na
\sectioneng{IEEE Transactions on Nuclear Science}, volume 51, número
3. \cite{aa:tns-2004-3}.

>>>>

\paragraph{Agosto de 2006: \sectioneng{Deployment of the ATLAS High-Level
Trigger}}, IEEE Transactions on Nuclear Science. Referência~\cite{aa:tns-06}

@@

\paragraph{Maio de 2006: \sectioneng{A configuration system for the ATLAS
trigger}}, Journal of Instrumentation, Maio de
2006. Referência~\cite{aa:jinst-06}

@@

\paragraph{Fevereiro de 2006: \sectioneng{Testing on a Large Scale : running
the ATLAS Data Acquisition and High Level Trigger Software on 700 PC Nodes}}
Computing In High Energy and Nuclear Physics  CHEP 2006 , Mumbai, India , 13 -
17 Feb 2006. Referência~\cite{aa:chep-06-01}

@@

\begin{quotation}
The ATLAS experiment at the Large Hadron Collider (LHC) will face the
challenge of efficiently selecting interesting candidate events in pp
collisions at 14 TeV center of mass energy, while rejecting the enormous
number of background events, stemming from an interaction rate of up to $10^9$
Hz. The First Level trigger will reduce this rate to around O(100
kHz). Subsequently, the High Level Trigger (HLT), which is comprised of the
Second Level trigger and the Event Filter, will need to further reduce this
rate by a factor of O($10^3$). The HLT selection is software based and will be
implemented on commercial CPUs, using a common framework built on the standard
ATLAS object oriented software architecture. In this paper an overview of the
current implementation of the selection for electrons and photons in the HLT
is given. The performance of this implementation has been evaluated using
Monte Carlo simulations in terms of the efficiency for the signal channels,
rate expected for the selection, data preparation times, and algorithm
execution times. Besides the efficiency and rate estimates, some physics
examples will be discussed, showing that the triggers are well adapted for the
physics programme envisaged at LHC. The electron and photon trigger software
is also being exercised at the ATLAS 2004 Combined Test Beam, where components
from all ATLAS subdetectors are taking data together along the H8 SPS
extraction line; from these tests a validation of the selection architecture
chosen in a real on-line environment is expected.
\end{quotation}

\paragraph{Junho de 2004: \sectioneng{Algorithms for the ATLAS high-level
trigger}}. Referência~\cite{aa:tns-04-05}

@@

\paragraph{Junho de 2004: \sectioneng{The base-line DataFlow system of the ATLAS
Trigger and DAQ}} Na revista \sectioneng{IEEE Transactions on Nuclear
Science}, volume 51, número 3. Referência~\cite{aa:tns-2004-3}

\begin{quotation}
The baseline design and implementation of the ATLAS DAQ DataFlow system is
described. The main components realizing the DataFlow system, their
interactions, bandwidths and rates are being discussed and performance
measurements on a 10\% scale prototype for the final Atlas TDAQ DataFlow
system are presented.

This prototype is a combination of custom design components and of
multi-threaded software applications implemented in C++ and running in a Linux
environment on commercially available PCs interconnected by a fully switched
gigabit Ethernet network.
\end{quotation}

\paragraph{Junho de 2004: \sectioneng{ATLAS TDAQ data collection software}} na
\sectioneng{IEEE Transactions on Nuclear Science}, volume 51, número
3. \cite{aa:tns-2004-3}.
